Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-13 latex_files/applied_network_science_article/article_v0.tex
update algorithm in article

@@

>>>>

\usepackage{algpseudocode}
\usepackage{algorithm}

@@

\subsection{Algorithm pseudo-code}
\label{algo}
\begin{algorithm}[H]
	\caption{Compute the transportation flow matrix $\mathbf{N} = (n_{st})$ knowing the edge-trip incidence matrix $\bm{\chi} = (\chi_{ij}^{st})$, the embarking flow $\mathbf{a}$, the disambarking flow $\mathbf{b}$, the index of an isolated source node $\tilde{s}$, and the minimum proportion of passengers entering/leaving the network hyperparameter $\theta$.}
	\label{algo1}
	\begin{algorithmic}[1]
		\State $g_{st} \leftarrow I(\chi_{\bullet \bullet}^{st} > 0) / \sum_{s't'}I(\chi_{\bullet \bullet}^{s't'} > 0), \; \forall s,t$ \Comment{{\footnotesize Initialize the prior distribution.}}
		\State $\alpha_s \leftarrow a_s / a_\bullet ,\; \beta_t \leftarrow b_t / b_\bullet, \; \forall s,t$ \Comment{{\footnotesize Initialize the margin distributions.}}
		\State $\epsilon \leftarrow 10^{-40}$ \Comment{{\footnotesize Fix a small quantity}}
		\While{$\mathbf{N} = (n_{st})$ has not converge} \Comment{{\footnotesize Main loop.}}
			\State $\psi_t \leftarrow 1, \; \forall t$ \Comment{{\footnotesize Initialize the lagragian multiplier for destinations.}}
			\While{$\bm{\psi} = (\psi_t)$ has not converge} \Comment{{\footnotesize Iterative fitting loop.}}
				\State $\phi_s \leftarrow \alpha_s / (\sum_t \psi_t g_{st} + \epsilon), \; \forall s$
				\State $\psi_t \leftarrow \beta_t / (\sum_s \phi_s g_{st} + \epsilon), \; \forall t$
			\EndWhile

			\State $n_{st} \leftarrow \frac{a_{\tilde{s}}}{\alpha_{\tilde{s}}} \phi_s \psi_t g_{st}, \; \forall s,t$ \Comment{{\footnotesize Compute the transportation flow.}}

		\EndWhile
		\State \Return $\mathbf{Z}$
	\end{algorithmic}
\end{algorithm}
